---
title: "Case Study 2"
author: "Tricia Herrera"
date: "08/07/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)



library(dplyr)
library(tidyverse)
library(VIM)
library(caret)
library(corrplot)
library(ggplot2) 
library(ggthemes)
library(gmodels)
library(gridExtra)
library(readr)
library(reshape2)
library(GGally)
library(ggcorrplot)
library(ggplot2)
library(visreg)
library(reshape2)
library(GGally)



CaseStudy2 <- read.csv("~/SMU/DS 6306/Case Study 2/CaseStudy2-data.csv")

head(CaseStudy2)

#examine format of each variable
str(CaseStudy2)


#convert character values into factors 
CaseStudy2$Attrition <- as.factor(CaseStudy2$Attrition)
CaseStudy2$BusinessTravel <- as.factor(CaseStudy2$BusinessTravel)
CaseStudy2$Department <- as.factor(CaseStudy2$Department)
CaseStudy2$EducationField <- as.factor(CaseStudy2$EducationField)
CaseStudy2$Gender <- as.factor(CaseStudy2$Gender)
CaseStudy2$JobRole <- as.factor(CaseStudy2$JobRole)
CaseStudy2$MaritalStatus <- as.factor(CaseStudy2$MaritalStatus)
CaseStudy2$Over18 <- as.factor(CaseStudy2$Over18)
CaseStudy2$OverTime <- as.factor(CaseStudy2$OverTime)
CaseStudy2$Education <- as.factor(CaseStudy2$Education)
CaseStudy2$JobInvolvement <- as.factor(CaseStudy2$JobInvolvement)
CaseStudy2$JobLevel <- as.factor(CaseStudy2$JobLevel)
CaseStudy2$JobSatisfaction <- as.factor(CaseStudy2$JobSatisfaction)
CaseStudy2$RelationshipSatisfaction <- as.factor(CaseStudy2$RelationshipSatisfaction)
CaseStudy2$StockOptionLevel <- as.factor(CaseStudy2$StockOptionLevel)
CaseStudy2$WorkLifeBalance <- as.factor(CaseStudy2$WorkLifeBalance)
CaseStudy2$EnvironmentSatisfaction <- as.factor(CaseStudy2$EnvironmentSatisfaction)

str(CaseStudy2)


#Remove the following columns: Over18, Employee Count & Standard Hours and Performance Rating that did not add value 
my_data = CaseStudy2[setdiff(colnames(CaseStudy2), c('Over18', 'StandardHours','EmployeeCount', 'EmployeeNumber', 'PerformanceRating'))]


```

Before we dived into the analysis we did some little pre processing of the data to identify any NAs. Luckily for us there is no NA values. 
```{r}
#Quick NA count
MissingValues <- sapply(my_data, function(MissingValue)sum(is.na(MissingValue)))
view(MissingValues)
```


To get a global view of a of daily rate, hourly rate, monthly income and monthly rate at once, a scatter plot matrix can be viewed. The red values are No on attrition and Blue are Yes.  We can see that there is not much correlation between daily rate, hourly rate and monthly rate in terms of attrition. We can also see that there isn't much difference within the variables  themselves as most of the box plots are of the same size. Lastly we don't see any correlation among each other.  Since there is not much information about these predictors nor do they appear to add value they will be ommited from the analysis. 



```{r}

ggpairs(my_data,columns=c('DailyRate', 'HourlyRate','MonthlyRate', 'MonthlyIncome'),aes(colour=Attrition))


my_data2 = my_data[setdiff(colnames(my_data), c('DailyRate', 'HourlyRate','MonthlyRate'))]
dim(my_data2)


```


```{r}
#Creating a categorical response for monthly income for illustrative purposes.

my_data2$MonthlyIncomecat<-factor(ifelse(my_data2$MonthlyIncome>median(my_data2$MonthlyIncome),"High","Low"),levels=c("Low","High"))
#last level is the success

```
We can explore continuous variables to determine if there is any variables that may not add value to our analysis because there s not a difference in means between attrition. 
```{r}

#explore continuous variables 
t1 <- my_data2 %>% 
    ggplot(aes(x = Attrition,
               y = DistanceFromHome,
               fill = Attrition)) +
    geom_boxplot() + 
    scale_fill_few(palette = 'Light') +
  theme_few()
  
    
t2 <- my_data2 %>% 
    ggplot(aes(x = Attrition,
               y = Age,
               fill = Attrition)) +
    geom_boxplot() + 
    scale_fill_few(palette = 'Light') +
  theme_few()    
    
    
t3 <- my_data2 %>% 
    ggplot(aes(x = Attrition,
               y = NumCompaniesWorked,
               fill = Attrition)) +
    geom_boxplot() + 
    scale_fill_few(palette = 'Light') +
    theme_few()
  
  
t4 <- my_data2 %>% 
    ggplot(aes(x = Attrition,
               y = TotalWorkingYears,
               fill = Attrition)) +
    geom_boxplot() + 
    scale_fill_few(palette = 'Light') + 
    theme_few()
  
t5 <- my_data2 %>% 
    ggplot(aes(x = Attrition,
               y = TrainingTimesLastYear,
               fill = Attrition)) +
    geom_boxplot() + 
    scale_fill_few(palette = 'Light') + 
    theme_few()

t6 <- my_data2 %>% 
    ggplot(aes(x = Attrition,
               y = YearsAtCompany,
               fill = Attrition)) +
    geom_boxplot() + 
    scale_fill_few(palette = 'Light') + 
    theme_few()

t7 <- my_data2 %>% 
    ggplot(aes(x = Attrition,
               y = YearsInCurrentRole,
               fill = Attrition)) +
    geom_boxplot() + 
    scale_fill_few(palette = 'Light') + 
    theme_few()
  
t8 <- my_data2 %>% 
    ggplot(aes(x = Attrition,
               y = YearsSinceLastPromotion,
               fill = Attrition)) +
    geom_boxplot() + 
    scale_fill_few(palette = 'Light') + 
    theme_few()

t9 <- my_data2 %>% 
    ggplot(aes(x = Attrition,
               y = YearsWithCurrManager,
               fill = Attrition)) +
    geom_boxplot() + 
    scale_fill_few(palette = 'Light') + 
    theme_few()
  
t10 <- my_data2 %>% 
    ggplot(aes(x = Attrition,
               y = MonthlyIncome,
               fill = Attrition)) +
    geom_boxplot() + 
    scale_fill_few(palette = 'Light') + 
    theme_few()
  
t<-grid.arrange(t1, t2, t3, t4, t5, t6, t7, t8, t9, t10)





```


There appears that there inst much of a difference between Age, Percent Salary Hike, Years Since Last Promotion and Attrition variables. We can explore this more by doing a  t test for these variables and if there is no difference between means we will remove these variables as they are not good predictors. After performing a Welch's t test we can reject the null hypothesis for Age only and fail to reject the null hypothesis for Percent Salary Hike and Years Since Last Promotion. There is significant evidence to suggest that there is a difference between age for Attrition Yes and No. Since we failed to reject the null hypothesis for Percent Salary Hike and Years Since Last Promotion this suggest that there is no difference in Attrition between these two variables so they will be removed from our analysis as predictors. 



``` {r}


t.test(my_data2$Age~my_data2$Attrition)


t.test(my_data2$PercentSalaryHike~my_data2$Attrition)


t.test(my_data2$YearsSinceLastPromotion~my_data2$Attrition)

my_data3 = my_data2[setdiff(colnames(my_data2), c('YearsSinceLastPromotion', 'PercentSalaryHike'))]
dim(my_data3)


```

We can not explore relationships between continuous variables by using a scatter plot and correlation matrix. It gives a board overview of correlations between continuous variables.
```{r}

#my_data3$AttritionBin <- ifelse(my_data3$Attrition == "Yes",1,0)


#my_data3corr = my_data3[setdiff(colnames(my_data3), c('Attrition','ID'))]


#my_data3_numericcorr <- dplyr::select_if(my_data3corr, is.numeric)


heatmap.cor <- function(df){
  df %>%
    keep(is.numeric) %>%
    drop_na() %>%
    cor %>%
    corrplot( addCoef.col = 'white',
             number.digits = 2,
             number.cex = 0.5,
             method = 'square')
}
heatmap.cor(my_data3)


ggpairs(my_data3,columns=c('YearsAtCompany','TotalWorkingYears','YearsInCurrentRole' , 'YearsWithCurrManager'),aes(colour=Attrition))


my_data3 = my_data3[setdiff(colnames(my_data3), c('TotalWorkingYears','YearsInCurrentRole' , 'YearsWithCurrManager'))]


```

Now we can explore the continuous variables to determine if they need to be transformed by using a histogram.
Some variables have a bit of a right skew but nothing too drastic we will assume normality and proceed with caution. 

```{r}
# histogram of all numeric variables
my_data3 %>% keep(is.numeric) %>% gather %>% ggplot(aes(x = value)) + facet_wrap(~key, scales = "free")+ geom_histogram() 

```
We then proceeded to do the same EDA for categorical variables. 
```{r}
#cross table to look at cat variables to see how they relate to the response 

#my_data3_factor <- dplyr::select_if(my_data3, is.factor)

#CrossTable(my_data3$Department, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)


#CrossTable(my_data3$EnvironmentSatisfaction, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)


#CrossTable(my_data3$JobRole, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)


#CrossTable(my_data3$Gender, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)


#CrossTable(my_data3$MaritalStatus, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)


#CrossTable(my_data3$RelationshipSatisfaction, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)



#CrossTable(my_data3$WorkLifeBalance, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)



#CrossTable(my_data3$MonthlyIncomecat, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)



#CrossTable(my_data3$EducationField, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)


#CrossTable(my_data3$BusinessTravel, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)



#CrossTable(my_data3$StockOptionLevel, my_data3$Attrition, prop.r = TRUE, prop.c = FALSE, prop.chisq = FALSE)
```
Quick visuals of factor variables to determine if there is any correlation between factors and attrition 
```{r}
 ggplot(my_data3, aes(EducationField, fill = Attrition)) + geom_bar()


ggplot(my_data3, aes(JobLevel, fill = Attrition)) + geom_bar()


 ggplot(my_data3, aes(x = Gender, fill = Attrition)) + 
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 90))


ggplot(my_data3, aes(x = MaritalStatus, fill = Attrition)) + 
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 90)) 

ggplot(my_data3, aes(EnvironmentSatisfaction, fill = Attrition)) + geom_bar() 


ggplot(my_data3, aes(JobRole, fill = Attrition)) + geom_bar() -> h3


ggplot(my_data3, aes(x = MonthlyIncomecat, fill = Attrition)) + 
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 90))


ggplot(my_data3, aes(x = BusinessTravel, fill = Attrition)) + 
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 90))



ggplot(my_data3, aes(RelationshipSatisfaction, fill = Attrition)) + geom_bar()


ggplot(my_data3, aes(Department, fill = Attrition)) + geom_bar()


ggplot(my_data3, aes(x = Education, fill = Attrition)) + 
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 90))


ggplot(my_data3, aes(x = JobInvolvement, fill = Attrition)) + 
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 90))

ggplot(my_data3, aes(x = StockOptionLevel, fill = Attrition)) + 
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 90))


ggplot(my_data3, aes(Gender, fill = Attrition)) + geom_bar()
ggplot(my_data3, aes(MaritalStatus, fill = Attrition)) + geom_bar()

ggplot(my_data3, aes(WorkLifeBalance, fill = Attrition)) + geom_bar()
```




The top three factors that were identified to be the highest contributor were: 1. OverTimeYes, JobLevel 5 BusinessTravel_TravelFrequently. 

```{r}

library(MASS)
library(tidyverse)
library(car)



my_data4 = my_data3[setdiff(colnames(my_data3), c('ID', 'MonthlyIncomecat', 'OverTimeDummy', 'GenderDummy', 'AttritionBin'))]

my_data4$AttritionBin <- ifelse(my_data3$Attrition == "Yes",1,0)

standardize = preProcess(my_data4, method = c("center", "scale"))
standardized.my_data3 = predict(standardize, my_data4)


full.log<-glm(Attrition~., data = my_data4, family = binomial('logit'), maxit = 100)

summary(full.log)

exp(cbind("Odds ratio" = coef(full.log), confint.default(full.log, level = 0.95)))

step.log<-full.log %>% stepAIC(trace=FALSE)

summary(step.log)
exp(cbind("Odds ratio" = coef(step.log), confint.default(step.log, level = 0.95)))


```

Identify job role specific trends that may exist in the data set 

```{r}

#Job role and Monthly Income
ggplot(data = my_data3, aes(x = JobRole, fill = MonthlyIncomecat)) +
    geom_bar(position = "fill") + ggtitle("Income By JobRole") +
  theme(axis.text.x=element_text(size=rel(0.8), angle=90)) + labs(x="Occupation",y="Proportion")


#Job role and Attrition
ggplot(data = my_data3, aes(x = JobRole, fill = Attrition)) +
    geom_bar(position = "fill") + ggtitle("Attrition By JobRole") +
  theme(axis.text.x=element_text(size=rel(0.8), angle=90)) + labs(x="Occupation",y="Proportion")

#Job role and Gender

ggplot(data = my_data3, aes(x = JobRole, fill = Gender)) +
    geom_bar(position = "fill") + ggtitle("Gender By JobRole") +
  theme(axis.text.x=element_text(size=rel(0.8), angle=90)) + labs(x="Occupation",y="Proportion")


#Job role and YearsAtCompany

ggplot(data = my_data3, aes(x = JobRole, fill = MaritalStatus)) +
    geom_bar(position = "fill") + ggtitle("TrainingTimesLastYear By JobRole") +
  theme(axis.text.x=element_text(size=rel(0.8), angle=90)) + labs(x="Occupation",y="Proportion")

#Job role and Job Satistication 

ggplot(data = my_data3, aes(x = JobRole, fill = JobSatisfaction)) +
    geom_bar(position = "fill") + ggtitle("JobSatisfaction By JobRole") +
  theme(axis.text.x=element_text(size=rel(0.8), angle=90)) + labs(x="Occupation",y="Proportion")

#Job role and  StockOptionLevel 

ggplot(data = my_data3, aes(x = JobRole, fill = StockOptionLevel)) +
    geom_bar(position = "fill") + ggtitle("StockOptionLevel by JobRole") +
  theme(axis.text.x=element_text(size=rel(0.8), angle=90)) + labs(x="Occupation",y="Proportion")




```
Provide any other interesting trends and observations from your analysis

```{r}

my_data3glm <- glm(Attrition ~ .,
                 family="binomial", 
                 data=my_data3)

#Attrition for Age
visreg(my_data3glm, "Age", 
       gg = TRUE, 
       scale="response", partial=FALSE, rug=FALSE) +
  labs(y = "Prob(Attrition)", 
       x = "Age",
       title = "Relationship of Age and Attrition")

#Attrition for Years At company
visreg(my_data3glm, "YearsAtCompany", 
       gg = TRUE, 
       scale="response", partial=FALSE, rug=FALSE) +
  labs(y = "Prob(Attrition)", 
       x = "YearsAtCompany",
       title = "Relationship of YearsAtCompany and Attrition")


#Attrition for Monthly Income 
visreg(my_data3glm, "MonthlyIncome", 
       gg = TRUE, 
       scale="response", partial=FALSE, rug=FALSE) +
  labs(y = "Prob(Attrition)", 
       x = "MonthlyIncome",
       title = "Relationship of MonthlyIncome and Attrition") + theme(axis.text.x=element_text(size=rel(0.8), angle=90))


#Attrition for Distance From Home   
visreg(my_data3glm, "DistanceFromHome", 
       gg = TRUE, 
       scale="response", partial=FALSE, rug=FALSE) +
  labs(y = "Prob(Attrition)", 
       x = "DistanceFromHome",
       title = "Relationship of DistanceFromHome and Attrition") + theme(axis.text.x=element_text(size=rel(0.8), angle=90))


#Attrition for WorkLifeBalance
visreg(my_data3glm, "WorkLifeBalance", 
       gg = TRUE, 
       scale="response", partial=FALSE, rug=FALSE) +
  labs(y = "Prob(Attrition)", 
       x = "WorkLifeBalance",
       title = "Relationship of WorkLifeBalance and Attrition") + theme(axis.text.x=element_text(size=rel(0.8), angle=90))

#Attrition for JobSatisfaction
visreg(my_data3glm, "JobSatisfaction", 
       gg = TRUE, 
       scale="response", partial=FALSE, rug=FALSE) +
  labs(y = "Prob(Attrition)", 
       x = "Job Role",
       title = "Relationship of JobSatisfaction and Attrition") + theme(axis.text.x=element_text(size=rel(0.8), angle=90))

#Attrition for StockOptionLevel
visreg(my_data3glm, "StockOptionLevel", 
       gg = TRUE, 
       scale="response", partial=FALSE, rug=FALSE) +
  labs(y = "Prob(Attrition)", 
       x = "Job Role",
       title = "Relationship of StockOptionLevel and Attrition") + theme(axis.text.x=element_text(size=rel(0.8), angle=90))

#Attrition for MaritalStatus
visreg(my_data3glm, "MaritalStatus", 
       gg = TRUE, 
       scale="response", partial=FALSE, rug=FALSE) +
  labs(y = "Prob(Attrition)", 
       x = "Job Role",
       title = "Relationship of MaritalStatus and Attrition") + theme(axis.text.x=element_text(size=rel(0.8), angle=90))



```

Naive Bayes model and prediction as well as prediction output.
```{r}
library(e1071)
set.seed(5678)
PredictionData = my_data3[setdiff(colnames(my_data3), c('ID', 'MonthlyIncomecat', 'OverTimeDummy', 'GenderDummy'))]
attrition.vector <- createDataPartition(PredictionData$Attrition, p = 0.6, list = F)
attrition.train <- PredictionData[attrition.vector,] 
attrition.test <- PredictionData[-attrition.vector,]


model = naiveBayes(Attrition~.,data = attrition.train)

#predict(model,attrition.test) #classifications
attrition.test$AttritionPrediction <- predict(model, attrition.test) #, type = "raw") #gives probabilities

confusionMatrix(
  table(attrition.test$Attrition, attrition.test$AttritionPrediction )
)

CaseStudy2CompSet.No.Attrition <- read.csv("~/SMU/DS 6306/Case Study 2/CaseStudy2CompSet No Attrition.csv")
attrition_pred <- CaseStudy2CompSet.No.Attrition

attrition_pred$BusinessTravel <- as.factor(attrition_pred$BusinessTravel)
attrition_pred$Department <- as.factor(attrition_pred$Department)
attrition_pred$EducationField <- as.factor(attrition_pred$EducationField)
attrition_pred$Gender <- as.factor(attrition_pred$Gender)
attrition_pred$JobRole <- as.factor(attrition_pred$JobRole)
attrition_pred$MaritalStatus <- as.factor(attrition_pred$MaritalStatus)
attrition_pred$Over18 <- as.factor(attrition_pred$Over18)
attrition_pred$OverTime <- as.factor(attrition_pred$OverTime)
attrition_pred$Education <- as.factor(attrition_pred$Education)
attrition_pred$JobInvolvement <- as.factor(attrition_pred$JobInvolvement)
attrition_pred$JobLevel <- as.factor(attrition_pred$JobLevel)
attrition_pred$JobSatisfaction <- as.factor(attrition_pred$JobSatisfaction)
attrition_pred$RelationshipSatisfaction <- as.factor(attrition_pred$RelationshipSatisfaction)
attrition_pred$StockOptionLevel <- as.factor(attrition_pred$StockOptionLevel)
attrition_pred$WorkLifeBalance <- as.factor(attrition_pred$WorkLifeBalance)
attrition_pred$EnvironmentSatisfaction <- as.factor(attrition_pred$EnvironmentSatisfaction)


str(attrition_pred)
head(attrition_pred) 

# generating predictions on test data
attrition_pred$attrition_pred <- predict(model, attrition_pred)


write.csv(attrition_pred, "C:/Users/18189/Documents/SMU/DS 6306/Case Study 2/CaseStudy2ClassifciationPreddictionTriciaHerrera.csv")

```

Second model for comparison against Naive Bayes  
```{r}

#Logistic Regression Model comparison 
attrition.LogReg <- trainControl(
 method = "repeatedcv",
 number = 5,
 repeats = 25,
 summaryFunction = twoClassSummary,
 classProbs = TRUE
)
#LogReg on Training Set
attrition.LogRegTrain <- train(
  Attrition ~ .,
  data = attrition.train,
 method = "LogitBoost",
   metric = "Spec",
  trControl = attrition.LogReg,
  preProcess = c("center","scale"),
 tuneLength = 6
)

# Adding predictions to Test Data
predict(attrition.LogRegTrain, newdata = attrition.test ) -> attrition.test$Attrition_LogReg
# creating confusion matrix
confusionMatrix(
  table(attrition.test$Attrition, attrition.test$Attrition_LogReg )
)



```
Linear regression model to predict Monthly Income. RMSE output generated. 

```{r}
set.seed(1234)

LMPrediction <- my_data3[, c(2,4,6,7,9,11,12,14,16,17,19,20,21,22,23)] 



monthlyincome.vector <- createDataPartition(LMPrediction$MonthlyIncome, p = 0.6, list = F)
monthlyincome.train <- LMPrediction[monthlyincome.vector,] 
monthlyincome.test <- LMPrediction[-monthlyincome.vector,]


#Linear Regression Prediction

#LM on Training Set


MonthlyIncome.LM <- lm(MonthlyIncome ~ ., data = monthlyincome.train)

# Final model
summary(MonthlyIncome.LM)
# Results including RMSE of final model
MonthlyIncome.LM$results

monthlyincome.test$MonthlyIncome_predict <- predict(MonthlyIncome.LM, newdata = monthlyincome.test)

error = monthlyincome.test$MonthlyIncome-monthlyincome.test$MonthlyIncome_predict
RMSE = sqrt(mean(error^2))
RMSE


#data below was causing my knit file to halt. Didn't feel it added value to mark down. 

# loading prediction data
#library(readxl)
#CaseStudy2CompSet_No_Salary <- read_excel("SMU/DS 6306/Case Study 2/CaseStudy2CompSet No Salary.xlsx")
#monthlyincome_pred <- CaseStudy2CompSet_No_Salary

#monthlyincome_pred$Attrition <- as.factor(monthlyincome_pred$Attrition)
#monthlyincome_pred$BusinessTravel <- as.factor(monthlyincome_pred$BusinessTravel)
#monthlyincome_pred$Department <- as.factor(monthlyincome_pred$Department)
#monthlyincome_pred$EducationField <- as.factor(monthlyincome_pred$EducationField)
#monthlyincome_pred$Gender <- as.factor(monthlyincome_pred$Gender)
#monthlyincome_pred$JobRole <- as.factor(monthlyincome_pred$JobRole)
#monthlyincome_pred$MaritalStatus <- as.factor(monthlyincome_pred$MaritalStatus)
#monthlyincome_pred$Over18 <- as.factor(monthlyincome_pred$Over18)
#monthlyincome_pred$OverTime <- as.factor(monthlyincome_pred$OverTime)
#monthlyincome_pred$Education <- as.factor(monthlyincome_pred$Education)
#monthlyincome_pred$JobInvolvement <- as.factor(monthlyincome_pred$JobInvolvement)
#monthlyincome_pred$JobLevel <- as.factor(monthlyincome_pred$JobLevel)
#monthlyincome_pred$JobSatisfaction <- as.factor(monthlyincome_pred$JobSatisfaction)
#monthlyincome_pred$RelationshipSatisfaction <- as.factor(monthlyincome_pred$RelationshipSatisfaction)
#monthlyincome_pred$StockOptionLevel <- as.factor(monthlyincome_pred$StockOptionLevel)
#monthlyincome_pred$WorkLifeBalance <- as.factor(monthlyincome_pred$WorkLifeBalance)
#monthlyincome_pred$EnvironmentSatisfaction <- as.factor(monthlyincome_pred$EnvironmentSatisfaction)


#str(monthlyincome_pred)
#head(monthlyincome_pred) 

# generating predictions on test data
#monthlyincome_pred$Monthly_incomepred <- predict(MonthlyIncome.LM, monthlyincome_pred)

#monthlyincome_predTH <- cbind(monthlyincome_pred)

#write.csv(monthlyincome_pred, "C:/Users/18189/Documents/SMU/DS 6306/Case Study 2/CaseStudy2RegressionPreddictionTriciaHerrera.csv")



```
